Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-11 krs-survey.tex
New proposed title + added Rachid to co-authors
Reorganized Kn Acq, introduced it

\title{Requirements and Current State of Knowledge Representation Systems for Service Robotics}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz}

@@

\paragraph{Linked Knowledge Resources}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf F. Knowledge instantiation}
            child {node [taxon] {{\bf F.4} Alignement with Standards}}
            child {node [taxon] {{\bf F.3} Self-Knowledge}}
            child {node [taxon] {{\bf F.2} Metrics}}
            child {node [taxon] {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

@@

Ontology engineering has grown into a research field of its own\fxwarning{Give
some idea about it? wikipedia?}.

@@

Several strategies ... Designing, implementing and feeding an ontological model of the beliefs of the robot

\begin{itemize}
    \item Dynamic, run-time instantiation
    \item Static, a priori knowledge
    \item Fetch from external resources (TBox and/or ABox)
\end{itemize}

@@

Qualitative and quantitative metrics give an oversight of the size and
expressive complexity of ontologies.

@@

\subsubsection{Alignment with Standard Upper-ontologies}

>>>>

\title{Knowledge Representation for Service Robots: Supply and Demand}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz, Rachid Alami}

@@

\paragraph{Linked Knowledge Resources}
\label{sect|lod}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[taxonomy]
    \node [taxon] {\bf F. Knowledge instantiation}
            child {node [taxon] {{\bf F.5} Self-Knowledge}}
            child {node [taxon] {{\bf F.4} Metrics}}
            child {node [taxon] {{\bf F.3} Granularity}}
            child {node [taxon] {{\bf F.2} Common-sense and Alignement}}
            child {node [taxon] {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

This last branch of our taxonomy looks at the actual \emph{content} of the
knowledge base: the knowledge instantiation. Here, \emph{instantiation} does
not only refer to the instantiation of the knowledge structure (what we have
called the ABox), but also includes the knowledge structure itself (the TBox).

While we have previously mentioned features of knowledge representation system
that enable the robot to fill its knowledge base with content and alter the
knowledge structure, most of the systems also come with a certain amount of
initial knowledge that often includes \emph{common-sense} knowledge (\ie facts
that widely known to humans, and hence often implicit: ``to put a cake in the
oven, one must first open the oven's door'').

The design strategy, the choice to rely on common-sense knowledge or not, the
reuse of standard ontologies, the quantity of {\it a priori} knowledge are many
parameters that lead to different knowledge models.

@@

Ontology engineering has grown into a research field of its own, covering
formalized methodologies for ontology creation, reuse, modularisation, etc.

The creation

@@

\subsubsection{Common-sense and alignment with Standard Upper-ontologies}

At section~\ref{sect|lod} we have presented how remote knowledge bases are a
valuable source of knowledge, including common-sense knowledge, that robot can
extract.

\subsubsection{Granularity}

The knowledge \emph{granularity} qualifies the level of details or refinement
of the knowledge stored.

...

The storage of literal values is a particular case: while knowledge
representation systems have been considered until now mostly as symbolic
systems, they can often represent literal values (in particular, numerical
values) as well.

Depending on the representation language, literal values can be naturally
represented and processed (common case in logic programming language) or not
(storing numerical value, let alone matrices, in OWL is cumbersome).

@@

Qualitative and quantitative metrics give an insight on the size and
expressive complexity of ontologies.

@@
